---
title: "Project2"
author: "Team 6"
date: "2024-04-09"
output: html_document
---

```{r warning = F, message = F}
library(tidyverse)
```




# Karthik
### Learning preference ( Qualitative -Nominal) - Bar plot
```{r}

```
### Lectures behind (Quantitative, Discrete) - Histogram
```{r}

```
### Play speed of lectures?  (Quantative, Discrete) - Histogram
```{r}

```
### Time before the due date do you submit assignments? ( Qualitative -Nominal) - Bar plot
```{r}

```


# Caleb
### Lectures behind (Quantitative, Discrete) and sleep time (Quantitative-Discrete)  - Scatter plot
```{r}

```
### Learning preference (Qualitative-Nominal)and lectures behind (Quantitative-Discrete)- Side-by-side box plot
```{r}

```
### Amount of extra-curricular  (Quantitative-Discrete) versus hours studying (Quantitative-Discrete) - Scatter plot
```{r}

```

# Ella 
### Play speed (Quantitative-Discrete) and amount spent studying (Quantitative-Discrete)- Scatter plot
```{r}

```
### Learning preference (Qualitative-Nominal) and time submitted before assignment (Qualitative-Ordinal) -Stacked bar plot
```{r}

```
### Play speed (Quantitative-Discrete) and time submitted before the assignment(Qualitative-Ordinal) - Side-by-side box plot
```{r}

```
