---
title: "Project2"
author: "Team 6"
date: "2024-04-09"
output: html_document
---

```{r warning = F, message = F}
library(tidyverse)
```

```{r}

surveyResults_1 = read.csv("~/Documents/GitHub/DATA1001/DATA1001 Project responses with time - Sheet1 copy.csv")
str(surveyResults_1)
```
```{r}
new_names = c("Timestamp","LearningPreference","CurrentLearningType","AssignmentSubmission","LecturesBehind","LectureSpeed","WakeUp","Bedtime","HoursStudying","Extracurriculars","MealsDaily","HoursSleep")
colnames(surveyResults_1) = new_names
rows_to_remove <- c(6,24,33)
surveyResults <- surveyResults_1[-rows_to_remove, ]

```

### Learning preference ( Qualitative -Nominal) - Bar plot
```{r}

ggplot(surveyResults, aes(x=LearningPreference)) + geom_bar()


```
### Lectures behind (Quantitative, Discrete) - Histogram
```{r}

ggplot(surveyResults, aes(x=LecturesBehind)) + geom_histogram()

```
### Play speed of lectures?  (Quantative, Discrete) - Histogram

changed to bar - please check
```{r}

ggplot(surveyResults, aes(x=LectureSpeed))  + geom_bar()

```
### Time before the due date do you submit assignments? ( Qualitative -Nominal) - Bar plot
```{r}
ggplot(surveyResults, aes(x=AssignmentSubmission))  + geom_bar()

```



### Lectures behind (Quantitative, Discrete) and sleep time (Quantitative-Discrete)  - Scatter plot
two just in case one shows better
```{r}

ggplot(surveyResults, aes(x=LecturesBehind, y = HoursSleep)) + geom_point()

ggplot(surveyResults, aes(x=HoursSleep, y = LecturesBehind)) + geom_point()
```
### Learning preference (Qualitative-Nominal)and lectures behind (Quantitative-Discrete)- Side-by-side box plot
```{r}

ggplot(data = surveyResults, aes(x = LearningPreference, y = LecturesBehind)) +
    geom_boxplot() +
    theme_minimal() +
    labs(title = "Box Plot of Lectures Behind by Learning Preference",
         x = "Learning Preference",
         y = "Lectures Behind")
       


ggplot(data = surveyResults, aes(x = LecturesBehind, y = LearningPreference)) +
    geom_boxplot() +
    theme_minimal() +
    labs(title = "Box Plot of Lectures Behind by Learning Preference",
         x = "Lectures Behind",
         y = "Learning Preference")


```
### Amount of extra-curricular  (Quantitative-Discrete) versus hours studying (Quantitative-Discrete) - Scatter plot

fix

```{r}


ggplot(surveyResults, aes(x=Extracurriculars, y = HoursStudying)) + geom_point()

ggplot(surveyResults, aes(x=HoursStudying, y = Extracurriculars)) + geom_point()
```

### Play speed (Quantitative-Discrete) and amount spent studying (Quantitative-Discrete)- Scatter plot
```{r}

ggplot(surveyResults, aes(x=LectureSpeed, y = HoursStudying)) + geom_point()


ggplot(surveyResults, aes(x=HoursStudying, y = LectureSpeed)) + geom_point()

```
### Learning preference (Qualitative-Nominal) and time submitted before assignment (Qualitative-Ordinal) -Stacked bar plot
```{r}

ggplot(surveyResults, aes(x=LearningPreference)) + geom_bar(aes(fill=AssignmentSubmission))

ggplot(surveyResults, aes(x=AssignmentSubmission)) + geom_bar(aes(fill=LearningPreference))


barplot(table(surveyResults$AssignmentSubmission,surveyResults$LearningPreference))

barplot(table(surveyResults$LearningPreference,surveyResults$AssignmentSubmission))


```
### Play speed (Quantitative-Discrete) and time submitted before the assignment(Qualitative-Ordinal) - Side-by-side box plot
```{r}

ggplot(surveyResults, aes(x=LectureSpeed, y = AssignmentSubmission)) + geom_boxplot()

ggplot(surveyResults, aes(x=AssignmentSubmission, y = LectureSpeed)) + geom_boxplot()


```
